\title{Publications}
\author{Perry Williams}
\date{}

\maketitle

\section*{Legend}
$^u$ = Undergraduate student advised \quad
$^g$ = Graduate student advised \quad
$^p$ = Post-doctoral fellow advised \quad
$^s$ = Senior author

\subsection*{Journal Articles}

\subsubsection*{In Review / Revision}
\begin{itemize}
\item Golden$^g$, JE, JG Barnes, and PJ Williams$^s$. \emph{In Review}. Estimating Survival and Population Trajectories of Golden Eagles in Nevada. \emph{Journal of Raptor Research}.
\item Acevedo$^g$, CR, PJ Williams$^s$, JS Sedinger, and T Dilts. \emph{In Review}. Spatio-temporal drivers of sage-grouse population change in Nevada. \emph{Ecology and Evolution}.
\item Shoemaker, KT, H Reich, PJ Williams, M Osterhout, J Vasquez, J Beckmann, C Lackey, KM Stewart. Late season frosts and changing snowpack may exacerbate human-bear conflicts. \emph{Ecosphere}.
\end{itemize}

\subsubsection*{Accepted}
\begin{itemize}
\item Brockman$^g$, JC, PS Coates, JC Tull, ST O'Neil, and PJ Williams$^s$. \emph{Accepted}. The effects of breeding status on common raven movement, home range, and habitat selection. \emph{The Journal of Wildlife Management}. \textbf{IF: 2.6}.
\item Wann, G, A Whipple, E Orning, M McLachlan, J Beck, PS Coates, C Conway, J Dinkins, A Johnston, C Hagen, P Makela, D Naugle, M Schroeder, J Sedinger, B Walker, PJ Williams, R Inman, C Aldridge. \emph{Accepted}. Greater sage-grouse seasonal habitat associations: A review and considerations for interpretation and management applications. \emph{The Journal of Wildlife Management}. \textbf{IF: 2.6}.
\end{itemize}

\subsubsection*{Published}
\begin{itemize}
\item Eisaguirre, JM, MG Lohman$^g$, GG Frye, HE Johnson, TV Riecke, \& PJ Williams$^s$. \emph{2025}. Estimating spatially explicit survival and mortality risk from telemetry data with thinned point process models. \emph{Ecology Letters} e70092. \textbf{IF: 7.6}.
\item Eisaguirre$^p$, JM, PJ Williams$^s$, and MB Hooten. 2024. Rayleigh step-selection functions and connections to coninuous-time mechanistic movement models. \emph{Movement Ecology}. 12:14 pages. \textbf{IF: 3.4}.
\item Blum$^p$, ME, JR Bennett, FE Buderman, KM Stewart, M Cox, and PJ Williams$^s$. 2024. Comparing contemorary models to traditional indices to estimate abundance of desert bighorn sheep. \emph{Journal of Wildlife Management}. 88:e22517. \textbf{IF: 2.6}.
\item Eisaguirre$^p$, JM, PJ Williams$^s$, X Lu, ML Kissling, PA Schuette, BP Weitzman, WS Beatty, GG Esslinger, JN Womble, and MB Hooten. 2023. Informing management of recovering predators and their prey with ecological diffusion models. \emph{Frontiers in Ecology and the Environment}. 21:479--488. \textbf{IF: 13.8}.
\item Eisaguirre$^p$, JM, PJ Williams$^s$, JC Brockman$^g$, SB Lewis, C Barger, G Breed, and T Booms. 2023. A hierarchical modeling framework for estimating individual- and population-level reproductive success from movement data. \emph{Methods in Ecology and Evolution}. 14:2110--2122. \textbf{IF: 8.3}.
\item Keating$^g$, MP, PJ Williams$^s$, JR Robb, FE Buderman, JP Lewis, T Vanosdol, and R Harer$^u$. 2023. Henslow's sparrow shows positive response to prescribed fire rotation. \emph{Ornithological Applications}. 125, duad018. \textbf{IF: 2.8}.
\item Williams$^s$, PJ, X Lu, HR Scharf, and MB Hooten. 2023. Embracing Asymmetry in Nature: How to account for skewness in ecological data. \emph{Ecological Informatics} 75:102085. \textbf{IF: 4.5}.
\item Riecke$^p$, TV, MG Lohman$^g$, BS Sedinger$^p$, TW Arnold, C Feldheim, DN Koons, F Rohwer, M Schaub, PJ Williams, and JS Sedinger. 2022. Density-dependence produces spurious relationships among demographic parameters in harvested species. \emph{Journal of Animal Ecology} 91:2261--2272. \textbf{IF: 5.6}. \href{https://besjournals.onlinelibrary.wiley.com/doi/10.1111/1365-2656.13807}{(Open Access)}.
\item Ellis$^u$, S, TV Riecke$^p$, MG Lohman$^g$, PJ Williams, JS Sedinger. 2022. Long-term trends and drought: spatiotemporal variation in juvenile sex ratios of North American ducks. \emph{Ecology and Evolution} 12:e9099. \textbf{IF: 3.2}. \href{https://onlinelibrary.wiley.com/doi/10.1002/ece3.9099}{(Open Access)}.
\item Riecke$^p$, TV, BS Sedinger$^p$, TW Arnold, D Gibson, DN Koons, MG Lowhman$^g$, M Schaub, PJ Williams, and JS Sedinger. 2022. A hierarchical model for jointly assessing ecological and anthropogenic impacts on animal demography. \emph{Journal of Animal Ecology} 91:1612--1626. \textbf{IF: 5.6}. \href{https://besjournals.onlinelibrary.wiley.com/doi/10.1111/1365-2656.13747}{(Open Access)}.
\item Street$^p$, PA, TV Riecke$^p$, PJ Williams, TL Behnke, and JS Sedinger. 2022. Estimating survival and adoption rates of dependent juveniles. \emph{Ecology and Evolution} 12:e9005. \textbf{IF: 3.2}. \href{https://onlinelibrary.wiley.com/doi/10.1002/ece3.9005}{(Open Access)}.
\item Koons, DN, TV Riecke$^p$, GS Boomer, BS Sedinger$^p$, JS Sedinger, PJ Williams, and TW Arnold. 2022. A niche model in adaptive resource management. \emph{Ecology and Evolution} 12:e8541. \textbf{IF: 3.2}. \href{https://onlinelibrary.wiley.com/doi/10.1002/ece3.8541}{(Open Access)}.
\item Scharf, HR, X Lu, PJ Williams, and MB Hooten. 2022. Constructing flexible, identifiable, and interpretable statistical models for binary data. \emph{International Statistical Review} 90:328--345. \textbf{IF: 1.9}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/scharf2022constructing.pdf}{(PDF)}.
\item O’Neil, ST, PS Coates, JC Brockman$^g$, PJ Jackson, JO Spencer, and PJ Williams$^s$. 2021. Inter- and intra-annual effects of lethal removal on common raven abundance in Nevada and California, USA. \emph{Human--Wildlife Interactions} 15:Iss.3, Article 20. \textbf{IF: 0.9}. \href{https://doi.org/10.26077/p79d-en84}{(Open Access)}.
\item Lohman$^g$, MG, TV Riecke$^p$, PJ Williams, and JS Sedinger. 2021. Individual heterogeneity in fitness in a long-lived herbivore. \emph{Ecology and Evolution} 11:15164--15173. \textbf{IF: 3.2}. \href{https://onlinelibrary.wiley.com/doi/10.1002/ece3.8197}{(Open Access)}.
\item Leach, CB, PJ Williams, JM Eisaguirre$^p$, JN Womble, MR Bower, and MB Hooten. 2021. Recursive Bayesian computation facilitates adaptive optimal design in ecological studies. \emph{Ecology} 103:e03573. \textbf{IF: 4.7}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/leach2021recurrsive.pdf}{(PDF)}.
\item Eisaguirre$^p$, JM, PJ Williams$^s$, X Lu, M Kissling, W. Beatty, GG Esslinger, JN Womble, and MB Hooten. 2021. Diffusion modeling reveals effects of multiple release sites and human activity on a recolonizing apex predator. \emph{Movement Ecology} 9:34. \textbf{IF: 5.3}. \href{https://movementecologyjournal.biomedcentral.com/articles/10.1186/s40462-021-00270-w}{(Open Access)}.
\item Womble, JN, PJ Williams$^s$, RW McNabb, A Prakash, R Gens, BS Sedinger$^p$, and CR Acevedo$^g$. 2021. Harbor seals as sentinels of Ice Dynamics in Tidewater Glacier Fjords. \emph{Frontiers in Marine Science} 8:634541. \textbf{IF: 5.2}. \href{https://www.frontiersin.org/articles/10.3389/fmars.2021.634541/full}{(Open Access)}.
\item Acevedo$^g$ CR, TV Riecke$^p$, AG Leach, MG Lohman$^g$, PJ Williams, and JS Sedinger. 2020. Long-term research and hierarchical models reveal consistent fitness costs of being the last egg in a clutch. \emph{Journal of Animal Ecology} 89:1978--1987. \textbf{IF: 5.6}. \href{https://besjournals.onlinelibrary.wiley.com/doi/10.1111/1365-2656.13232}{(Open Access)}.
\item Williams, PJ$^s$, C Schroeder, PJ Jackson. 2020. Estimating reproduction and survival of unmarked juveniles using aerial images and marked adults. \emph{Journal of Agricultural, Biological and Environmental Statistics} 25:133--147. \textbf{IF: 2.3}. \href{https://link.springer.com/article/10.1007/s13253-020-00384-5}{(Open Access)}.
\item Lu, Xinyi, PJ Williams, MB Hooten, JA Powell, JN Womble, and MR Bower. 2020. Nonlinear reaction-diffusion process models improve inference for population dynamics. \emph{Environmetrics} 31:e2604. \textbf{IF: 1.5}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/lu2020nonlinear.pdf}{(PDF)}.
\item Riecke$^p$, TV, BS Sedinger$^p$, PJ Williams, AG Leach, and JS Sedinger. 2019. Estimating correlations among demographic parameters in population models. \emph{Ecology and Evolution} 9:13521--13531. \textbf{IF: 3.2}. \href{https://onlinelibrary.wiley.com/doi/10.1002/ece3.5809}{(Open Access)}.
\item Williams, PJ, WL Kendall, and MB Hooten. 2019. Selecting ecological models using multi-objective optimization. \emph{Ecological Modelling} 404:21--26. \textbf{IF: 3.5}. \href{https://www.sciencedirect.com/science/article/pii/S0304380019301577?via%3Dihub}{(Open Access)}.
\item Riecke$^p$, TV, PJ Williams$^s$, TL Behnke, D Gibson, AG Leach, BS Sedinger$^p$, PA Street, and JS Sedinger. 2019. Integrated population models: model assumptions and inference. \emph{Methods in Ecology and Evolution} 10:1072--1082. \textbf{IF: 8.3}. \href{https://besjournals.onlinelibrary.wiley.com/doi/10.1111/2041-210X.13195}{Free Access}.
\item Williams$^s$, PJ, MB Hooten, GG Esslinger, JN Womble, JL Bodkin, and MR Bower. 2019. The rise of an apex predator following deglaciation. \emph{Diversity and Distributions} 25:895--908. \textbf{IF: 5.7}. \href{https://onlinelibrary.wiley.com/doi/10.1111/ddi.12908}{(Open Access)}.
\item Conn, PB, DS Johnson, PJ Williams, SR Melin, and MB Hooten. 2018. A guide to Bayesian model checking for ecologists. \emph{Ecological Monographs} 88:526--542. \textbf{IF: 9.8}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/conn2018guide.pdf}{(PDF)}.
\item Williams$^s$, PJ, MB Hooten, GG Esslinger, JN Womble, and MR Bower. 2018. Monitoring dynamic spatio-temporal ecological processes optimally. \emph{Ecology} 99:524--535. \textbf{IF: 4.7}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/williams2018monitoring.pdf}{(PDF)}.
\item Williams, PJ, MB Hooten, JN Womble, and MR Bower. 2017. Estimating occupancy and abundance using aerial images with imperfect detection. \emph{Methods in Ecology and Evolution} 8:1679--1689. \textbf{IF: 8.3}. \href{https://besjournals.onlinelibrary.wiley.com/doi/10.1111/2041-210X.12815}{(Free Access)}.
\item Williams, PJ, MB Hooten, JN Womble, GG Esslinger, and MR Bower. 2017. An integrated data model to estimate spatio-temporal occupancy, abundance, and colonization dynamics. \emph{Ecology} 98:328--336. \textbf{IF: 4.7}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/williams2017integrated.pdf}{(PDF)}.
\item Hefley, TJ, KM Broms, BM Brost, FE Buderman, SL Kay, HR Scharf, JR Tipton, PJ Williams, and MB Hooten. 2017. The basis function approach to modeling autocorrelation in ecological data. \emph{Ecology} 98:632--646. \textbf{IF: 4.7}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/hefley2017basis.pdf}{(PDF)}.
\item Williams, PJ, and WL Kendall. 2017. A guide to multi-objective optimization for ecologists with an application to cackling goose management. \emph{Ecological Modelling} 343:54--67. \textbf{IF: 3.5}. \href{https://www.sciencedirect.com/science/article/pii/S0304380016305610?via%3Dihub}{(Open Access)}.
\item Williams, PJ and MB Hooten. 2016. Combining statistical inference and decisions in ecology. \emph{Ecological Applications} 26:1930--1942. \textbf{IF: 6.1}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/williams2016combining.pdf}{(PDF)}.
\item Crimmins, SM, PC McKann, JR Robb, JP Lewis, T Vanosdol, BA Walker, PJ Williams and WE Thogmartin. 2016. Factors affecting Henslow's sparrow (\emph{Ammodramus henslowii}) nest survival in southern Indiana. \emph{Wilson Journal of Ornithology} 128. \textbf{IF: 0.5}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/crimmins2016factors.pdf}{(PDF)}.
\item Vigil, E, MKR Christianson, JM Lepak, and PJ Williams. 2016. Temperature effects on hatching and viability of juvenile gill lice, \emph{Salmincola californiensis}. \emph{Journal of Fish Diseases} 39:899--905. \textbf{IF: 2.8}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/vigel2016temperature.pdf}{(PDF)}.
\item Gerber, BD, PJ Williams, and LL Bailey. 2014. Primates and Cameras: Non-invasive sampling to make population-level inferences while accounting for imperfect detection. \emph{International Journal of Primatology} 35:841--858. \textbf{IF: 2.6}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/gerber2014noninvasive.pdf}{(PDF)}.
\item Williams, PJ, SH Whitmore, and RJ Guti\'errez. 2014. Use of private lands for foraging by California spotted owls in the central Sierra Nevada. \emph{Wildlife Society Bulletin} 38:705--709. \textbf{IF: 0.5}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/williams2014use.pdf}{(PDF)}.
\item Williams, PJ, NJ Engbrecht, JR Robb, VCK Terrell, and M. J. Lannoo. 2013. Surveying a threatened amphibian species through a narrow detection window. \emph{Copeia} 2013:552--561. \textbf{IF: 1.9}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/williams2013surveying.pdf}{(PDF)}.
\item Engbrecht, NJ, MJ Lannoo, PJ Williams, JR Robb, T Gerardot, DR Karns, and M Lodato. 2013. Is there hope for the Hoosier Frog? An update on the status of Crawfish Frogs (\emph{Lithobates areolatus}) in Indiana, with recommendations for their conservation. \emph{Proceedings of the Indiana Academy of Science} 121:147--157. \textbf{IF: 1.4}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/engbrecht2013hope.pdf}{(PDF)}.
\item Heemeyer, JL, PJ Williams, and MJ Lannoo. 2012. Obligate crayfish burrow use and core habitat requirements of crawfish frogs. \emph{Journal of Wildlife Management} 76:1081--1091. \textbf{IF: 2.6}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/heemeyer2012obligate.pdf}{(PDF)}.
\item Williams, PJ, JR Robb, and DR Karns. 2012. Habitat selection by crawfish frogs (\emph{Lithobates areolatus}) in a large mixed grassland/forest habitat. \emph{Journal of Herpetology} 46:682--688. \textbf{IF: 1.4}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/williams2012habitat.pdf}{(PDF)}.
\item Williams, PJ, JR Robb, and DR Karns. 2012. Occupancy dynamics of breeding crawfish frogs in southeastern Indiana. \emph{Wildlife Society Bulletin} 36:350--357. \textbf{IF: 0.5}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/Williams2012occupancy.pdf}{(PDF)}.
\item Williams, PJ, JR Robb, RH Kappler, TE Piening, and DR Karns. 2012. Intraspecific density dependence in larval development of the crawfish frog, \emph{Lithobates areolatus}. \emph{Herpetological Review} 43:36--38. \textbf{IF: 0.2}. \href{https://www.perrywilliams.us/wp-content/uploads/2018/03/williams2012intraspecific.pdf}{(PDF)}.
\item Williams, PJ, RJ Guti\'errez, and S Whitmore. 2011. Home range and habitat selection of the spotted owl in the central Sierra Nevada. \emph{Journal of Wildlife Management} 75:333--343. \textbf{IF: 2.6}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/williams2012home.pdf}{(PDF)}.
\item Hoffman, AS, J Heemeyer, PJ Williams, JR Robb, DR Karns, and MJ Lannoo. 2010. Strong site fidelity and a variety of imaging techniques reveal activity patterns in crawfish frogs (\emph{Lithobates areolatus}), a species of conservation concern. \emph{BioScience} 60:829--834. \textbf{IF: 11.6}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/hoffman2010strong.pdf}{(PDF)}.
\item Schook, DM, MD Collins, WE Jensen, PJ Williams, NE Bader, and TH Parker. 2008. Geographic patterns of song similarity in the Dickcissel. \emph{The Auk} 125:953--964. \textbf{IF: 1.0}. \href{http://www.perrywilliams.us/wp-content/uploads/2023/05/schook2008geographic.pdf}{(PDF)}.
\end{itemize}
